---
title       : Factor Analysis Slideshow
subtitle    : Boat Case
author      : Stratos Moschidis
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

```{r include=FALSE}
## load the FactoMineR library for factor analysis
library(FactoMineR)
## load the xtable library for table HTML output
library(xtable)
## load the Hmisc library for minor ticks in graphs
library(Hmisc)

## function to get the eigenvalues
getdataforeigentable <- function(eigenvalues, eigenvalues.limit) {
  data.for.eigentable <- c()

  for(i in 1:nrow(eigenvalues)){
    if(eigenvalues[i,1] > eigenvalues.limit){
      
    }else{
      data.for.eigentable <- eigenvalues[1:i-1,]
      break
    }
  }
  
  return(data.for.eigentable)
}

## function to get the corfacotr
getcorfactortable <- function(corfactor, corfactor.limit){
  for(i in 1:nrow(corfactor)){
    for(j in 1:ncol(corfactor)){
      if(corfactor[i,j] < corfactor.limit){
        corfactor[i,j] <- NA
      }
    }
  }
  return(corfactor)
}
```

### Load the dataset
Load the whole dataset into mydatatemp. We can set the eigenvalues limit for the output table and corfactor limit for output correlation table.

```{r}
mydatatemp <- read.csv("../../data/boat/boats.csv", header = TRUE)
eigenvalues.limit <- 1
corfactor.limit <- 0.4
```

Extract a subset of dataset to be used in Principal component analysis for Question 1. 
```{r}
mydata <- mydatatemp[,2:30]
```

--- .class #id 

### Principal Component Analysis
We used PCA function from FactoMineR package. Store the PCA results into result object as following.
```{r}
result <- PCA(mydata, graph=FALSE)
```

--- .class #id 

### Results

PCA results are stored in result object. Components of PCA can be accessed using following component names.


No |Name         |      Description                          
------------|-----|---------|-----------
1 | "$eig"        |     eigenvalues                        
2 | "$var"         |    results for the variables         
3 | "$var$coord"    |   coord. for the variables          
4 | "$var$cor"       |  correlations variables - dimensions
5 | "$var$cos2"      |   cos2 for the variables             
6 | "$var$contrib"    |  contributions of the variables 

--- .class #id 

### Continue

No |Name         |      Description                          
------------|-----|---------|-----------
7 | "$ind"        |      results for the individuals        
8 | "$ind$coord"   |     coord. for the individuals         
9 | "$ind$cos2"   |      cos2 for the individuals           
10 |"$ind$contrib"  |    contributions of the individuals  
11 |"$call"       |      summary statistics              
12 |"$call$centre"  |    mean of the variables            
13 |"$call$ecart.type" | standard error of the variables  
14 |"$call$row.w"    |   weights for the individuals        
15 |"$call$col.w"   |    weights for the variables

--- .class #id 

### Output and tables

#### 1. Eigen Values &amp; Percentage of Total Variance

Get the eigenvalues object. Create a table using xtable function from xtable library. However, we don't want to see all the data. We want to see only component which has eigenvalues greater than `r eigenvalues.limit`,

--- .class #id 


```{r comment=NA, results='asis'}
eigenvalues<-result$eig

data.for.eigentable <- getdataforeigentable(eigenvalues, eigenvalues.limit)

print(xtable(head(data.for.eigentable), digits=3), comment = FALSE, include.rownames = TRUE, type='HTML')

```

--- .class #id 

#### 2. Scree Plot
Generate a scree plot using following command. We assign the labels for x axis and y axis manually.
```{r fig.height=4,fig.align='center',fig.width=5}
## start to draw the plot
plot(eigenvalues$eigenvalue, type="o", xlab="Component Number", ylab="Eigenvalue", col=colors()[26], lwd=2)
## add minor ticks
minor.tick(nx=5, ny=2)
## add abline at y = 1
abline(h=1,lty=2,col=colors()[34]) 

```

--- .class #id 

#### 3. Correlation of old variables with new factors

Correlation matrix of each new factor with the initial variables can be accessed with $var$cor component in result object. Create a table using xtable function from xtable library. However, we don't want to see all the correlations but which has correlation coefficient greater than `r corfactor.limit`.

--- .class #id 

```{r results='asis'}
corfactor <- result$var$cor

corfactor <- getcorfactortable(corfactor, corfactor.limit)

print(xtable(head(corfactor), digits=3), comment = FALSE, include.rownames = TRUE, type='HTML')
```

--- .class #id 

#### 4. Matrix:Respondents - Factors

New matrix(number of respondents X number of factors) can be accessed at $ind$coord component of result object. First 10 rows are ouput as an example.

```{r results='asis'}
factormatrix <- result$ind$coord

print(xtable(head(factormatrix[1:10,]), digits=3), comment = FALSE, include.rownames = TRUE, type='HTML')
```

--- .class #id 

#### 5. Other interesting plots

```{r} 
plot(result$var$cos2)
```

```{r} 
plot(result$ind$cos2)
```
