<div class="container">
<html> 
  <head> 
    <script src="jquery.js"></script> 
    <script> 
    $(function(){
      $("#includedContent").load("include.html"); 
    });
    </script> 
  </head> 
  <body>
     <div id="includedContent"></div>
  </body> 
</html>


```{r echo=FALSE,include=FALSE,results='hide'}
library(xtable)
sal91 <- read.csv("C:/Users/STRATOS/Desktop/R/githubsite/data-analytics-course/data/session12/sal91.csv", sep=";")
fit1<-lm(SAL92~AGE,data=sal91)
printme11<-as.list(summary(fit1))
fit2<-lm(SAL92~EXPERI,data=sal91)
printme12<-as.list(summary(fit2))
fit3<-lm(SAL92~SEX,data=sal91)
printme13<-as.list(summary(fit3))
fit4<-lm(EXPERI~AGE,data=sal91)
printme14<-as.list(summary(fit4))
```

```{r  echo=FALSE,results='asis',warning=FALSE,error=FALSE,message=FALSE}

fm1<-xtable(summary(fit1),caption="Regression Analysis - Dependent variable SAL92")
print(fm1,type="html",html.table.attributes = "class='table table-striped table-hover table-bordered'",caption.placement="top")

```

Residual standard error: `r sqrt(deviance(fit1)/df.residual(fit1))` on `r fit1$df` degrees of freedom<br>
Multiple R-squared: `r printme11$r.squared` ,  Adjusted R-squared: `r printme11$adj.r.squared` <br>
F-statistic: `r printme11$fstatistic["value"]` on   `r printme11$fstatistic["numdf"]` and `r printme1$fstatistic["dendf"]` <br>
p-value: `r pf(printme11$fstatistic[1], printme11$fstatistic[2], printme11$fstatistic[3],lower.tail = FALSE)` <br><br>

```{r  echo=FALSE,results='asis',warning=FALSE,error=FALSE,message=FALSE}

fm2<-xtable(summary(fit2),caption="Regression Analysis - Dependent variable SAL92")
print(fm2,type="html",html.table.attributes = "class='table table-striped table-hover table-bordered'",caption.placement="top")

```

Residual standard error: `r sqrt(deviance(fit2)/df.residual(fit2))` on `r fit2$df` degrees of freedom<br>
Multiple R-squared: `r printme12$r.squared` ,  Adjusted R-squared: `r printme12$adj.r.squared` <br>
F-statistic: `r printme12$fstatistic["value"]` on   `r printme12$fstatistic["numdf"]` and `r printme12$fstatistic["dendf"]` <br>
p-value: `r pf(printme12$fstatistic[1], printme12$fstatistic[2], printme12$fstatistic[3],lower.tail = FALSE)` <br><br>

```{r  echo=FALSE,results='asis',warning=FALSE,error=FALSE,message=FALSE}

fm3<-xtable(summary(fit3),caption="Regression Analysis - Dependent variable SAL92")
print(fm3,type="html",html.table.attributes = "class='table table-striped table-hover table-bordered'",caption.placement="top")

```

Residual standard error: `r sqrt(deviance(fit3)/df.residual(fit3))` on `r fit3$df` degrees of freedom<br>
Multiple R-squared: `r printme13$r.squared` ,  Adjusted R-squared: `r printme13$adj.r.squared` <br>
F-statistic: `r printme13$fstatistic["value"]` on   `r printme13$fstatistic["numdf"]` and `r printme13$fstatistic["dendf"]` <br>
p-value: `r pf(printme13$fstatistic[1], printme13$fstatistic[2], printme13$fstatistic[3],lower.tail = FALSE)` <br><br>

```{r  echo=FALSE,results='asis',warning=FALSE,error=FALSE,message=FALSE}

fm4<-xtable(summary(fit4),caption="Regression Analysis - Dependent variable EXPERI")
print(fm4,type="html",html.table.attributes = "class='table table-striped table-hover table-bordered'",caption.placement="top")

```

Residual standard error: `r sqrt(deviance(fit4)/df.residual(fit4))` on `r fit4$df` degrees of freedom<br>
Multiple R-squared: `r printme14$r.squared` ,  Adjusted R-squared: `r printme14$adj.r.squared` <br>
F-statistic: `r printme14$fstatistic["value"]` on   `r printme14$fstatistic["numdf"]` and `r printme14$fstatistic["dendf"]` <br>
p-value: `r pf(printme14$fstatistic[1], printme14$fstatistic[2], printme14$fstatistic[3],lower.tail = FALSE)` <br><br><br>




</div>