<div class="container">
<html> 
  <head> 
    <script src="jquery.js"></script> 
    <script> 
    $(function(){
      $("#includedContent").load("include.html"); 
    });
    </script> 
  </head> 
  <body>
     <div id="includedContent"></div>
  </body> 
</html>

```{r echo=FALSE,include=FALSE,results='hide'}
source("../../code/session15/session15.R")
library(xtable)
```

```{r  echo=FALSE,results='asis',warning=FALSE,error=FALSE,message=FALSE}

session15<-xtable(summary(fit),caption="Regression Analysis")
print(session15,type="html",html.table.attributes = "class='table table-striped table-hover table-bordered'",caption.placement="top")

```
Residual standard error: `r sqrt(deviance(fit)/df.residual(fit))` on `r fit$df` degrees of freedom<br>
Multiple R-squared: `r fit$r.squared` ,  Adjusted R-squared: `r fit$adj.r.squared` <br>
F-statistic: `r fit$fstatistic["value"]` on   `r fit$fstatistic["numdf"]` and `r fit$fstatistic["dendf"]` <br>
p-value: `r pf(fit$fstatistic[1], fit$fstatistic[2], fit$fstatistic[3],lower.tail = FALSE)` <br><br><br>

```{r}
print(xtable(dwtest(fit)),type="html")
```

</div>